Paper_analyses

### 2021-09-05 Figures.Rmd
newplots

>>>>

p$graphstyle_tsne <-  theme(#base plot theme

  # axis lines
  # axis.line.y = element_line(color="black", size = 1.5),
  # axis.line.x = element_line(color="black", size = 1,5),

  # panel
  panel.grid.major = element_blank(),
   panel.border = element_rect(colour = "black", fill=NA, size=5),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="black"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),

  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)
?stat_ellipse

clustering_agg
clustering_agg$cluster_interpreted<- NULL
clustering_agg$AlexGroup<-NULL
clustering_agg$y_kmeans<-NULL

clustering_agg_JASPtest$stimIAPS2<- as.character(clustering_agg_JASPtest$stimIAPS2)
clust_stim2<- select(clustering_agg_JASPtest, c(stimIAPS2,clusters, stimDescription))

test<- left_join(clustering_agg,clust_stim2)

colnames(clustering_agg_JASPtest)
clustering_agg_JASPtest<- subset(clustering_agg_JASPtest, !is.na(clustering_agg_JASPtest$clusters))
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg_JASPtest$clusters)
plot_data$labels<- factor(plot_data$labels)
# stat_el
# plot_data$
plots_paper$PCA_clust

plot_data%>%
  subset(!is.na(labels))%>%
   # subset(!is.na(cluster))%>%
  ggplot( aes(x = PC1, y = PC2, colour = labels)) +
  geom_point(size = 1, alpha = .8)+
  # geom_text(aes(label= test$stimDescription), alpha = .7, size = 5)+
  # stat_ellipse()+
  # stat_ellipse(aes(x = PC1,y=PC2,
  #                  lty=labels,
  #                  fill=labels, 
  #                  color=labels),
  #   geom="polygon",
  #   alpha=0.2, 
  #   size = 1.5)+
  # scale_fill_manual(values=c("red","green","blue"))+
    # scale_color_manual(values=c("red","green","blue"))+
  # scale_linetype_manual(values=c(1,2,3))+
  ylab("Componet 2")+
  xlab("Component 1")+
  p$graphstyle +

theme(
  # axis.text.y   = element_text(size=14),
        # axis.text.x   = element_text(size=14),
        # axis.title.y  = element_text(size=14),
        # axis.title.x  = element_text(size=14),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=3)
  )

plots_paper$PCA_clust
ggsave("PCA_clust.tiff", plots_paper$PCA_clust , device = "tiff", width = 10, height = 7, dpi = 800)

clust_stim2
clustering_new <- left_join(clustering, clust_stim2, by = c("stimIAPS2", "stimDescription"))

clustering_new$Cluster<- clustering_new$clusters

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
clustering_new %>%
  subset(!is.na(Cluster))%>%
  # subset(ssid_num>303)%>%^
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "arousal",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective arousal \n (calm - agitated)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)
plots_paper$arousal_clust
# valence cluster

plots_paper$valence_clust<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  group_by(ssid, Cluster)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "Cluster", y = "valence",
          color = "Cluster")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  xlab("Cluster")+
  ylab("Subjective valence \n (negative - positive)")+
  p$graphstyle+ theme(legend.position = "none")
  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  # stat_compare_means(label.y = 9)

plots_paper$valence_clust

clust_subjective<- plots_paper$valence_clust+plots_paper$arousal_clust+
  plot_layout(ncol = 2)+plot_annotation(tag_levels = "A")

clust_subjective

ggsave("clust_subjective.tiff", clust_subjective, device = "tiff", width = 10, height = 5, dpi = 800)
```

### 2021-09-05 Paper_Analyses_subj_obje_arousal.Rmd
newplots

clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
colnames(clustering_agg)
clust_dataset = clustering_agg[c(20,24,25)]

@@

# Using the elbow method to find the optimal number of clusters
set.seed(6)
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(clust_dataset, i)$withinss)
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')

# Fitting K-Means to the dataset
set.seed(29)
kmeans = kmeans(x = clust_dataset, centers = 3)
y_kmeans = kmeans$cluster

@@

?clusplot
clusplot(clust_dataset,
         y_kmeans,
         lines = 2,
         shade = TRUE,
         color = TRUE,
         labels = 1,
         plotchar = FALSE,
         span = TRUE
         # label = 
         # main = paste('Clusters of customers'),
         # xlab = 'Annual Income',
         # ylab = 'Spending Score'
         )

@@

pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)

ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
  geom_point()+
  geom_text(aes(label= clustering_agg$stimDescription))

@@

tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "valence",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

options(scipen = 999)
tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "arousal",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

@@

cluster_lmers<- list()
clustering3$stimIAPS2<- as.factor(as.character(clustering3$stimIAPS2))

clustering3$ssid<- as.factor(as.character(clustering3$ssid))
clustering3

@@

clustering3$arousal

cluster_lmers$arousal <- lmer(arousal ~ cluster_interpreted + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

@@

emmeans::emmeans(cluster_lmers$arousal, pairwise~cluster_interpreted)

# valence
cluster_lmers$valence <- lmer(valence ~ cluster_interpreted + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

summary(cluster_lmers$valence)
emmeans::emmeans(cluster_lmers$valence, pairwise~cluster_interpreted)

>>>>

clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
colnames(clustering_agg)
clust_dataset = clustering_agg[c(25,24,20)]

@@

# Using the elbow method to find the optimal number of clusters
set.seed(1)
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(clust_dataset, i)$withinss)
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')

# Fitting K-Means to the dataset
set.seed(1)
kmeans = kmeans(x = clust_dataset, centers = 3)
y_kmeans = kmeans$cluster

@@

?clusplot

clust_dataset
y_kmeans
clusplot(clust_dataset,
         y_kmeans,
         lines = 2,
         shade = TRUE,
         color = TRUE,
         labels = 1,
         plotchar = FALSE,
         span = TRUE
         # label = 
         # main = paste('Clusters of customers'),
         # xlab = 'Annual Income',
         # ylab = 'Spending Score'
         )

test$Distances
```

@@

clust_dataset

clustering_agg%>%
  subset(y_kmeans == 3)%>%
  select(c(stimDescription))

clustering_agg_JASPtest%>%
   subset(clusters == 3)%>%
  select(c(stimDescription))

clustering_agg_bonkers <- subset(clustering_agg, stimIAPS2 != "9926")

pca_res <- prcomp(clustering_agg_bonkers[1:55,c(25,24,20)], center = TRUE, scale. = TRUE)
pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)

# plot_data$
ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
  geom_point(size = 2, alpha = .4)+
  # geom_text(aes(label= clustering_agg$stimDescription))+
  stat_ellipse(show.legend = TRUE)+
  ylab("Componet 2")+
  xlab("Component 1")+
  # scale_color_manual(values = c("red", "green", "blue"))+
  p$graphstyle+
  theme()

?scale_color_manual
scale_color_brewer(breaks=c("1","5","10","50","100"), palette = "Set1")
```

@@

tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "valence",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

options(scipen = 999)

```{r}
tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  group_by(ssid, cluster_interpreted)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(arousal2 = abs(arousal))%>%
  subset(arousal> -9)%>%
  ggboxplot(x = "cluster_interpreted", y = "arousal",
          color = "cluster_interpreted", palette = "jco")+
  geom_jitter(width = .1, alpha = .2)+
    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

@@

cluster_lmers<- list()
clustering_new$stimIAPS2<- as.factor(as.character(clustering_new$stimIAPS2))

clustering_new$ssid<- as.factor(as.character(clustering_new$ssid))
clustering3

@@

clustering3$arousal
clustering_new$Cluster<- as.factor(clustering_new$Cluster)
cluster_lmers$arousal <- lmer(arousal ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering_new)

@@

emmeans::emmeans(cluster_lmers$arousal, pairwise~Cluster)

# valence
cluster_lmers$valence <- lmer(valence ~ Cluster + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering_new)

summary(cluster_lmers$valence)
emmeans::emmeans(cluster_lmers$valence, pairwise~Cluster)

cluster_lmers$pup_clust <- lmer(pup_basCor ~ cluster_interpreted + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

cluster_lmers$pup_clust1 <- lmer(pup_basCor ~ y_kmeans + 
                               (1 | ssid)+
                               (1|stimIAPS2),
                             REML = FALSE,
                             data = clustering3)

summary(cluster_lmers$pup_clust1)

emmeans::emmeans(cluster_lmers$pup_clust1, pairwise~y_kmeans, adjust = "bonf")

table(is.na(clustering3$Bio_Mean_HR_dif))
cluster_lmers$hrdif_clust2 <- lmer(Bio_Mean_HR_dif ~ y_kmeans + 
                               (1 | ssid),
                               # <!-- (1|stimIAPS2), -->
                             REML = FALSE,
                             data = clustering3)

                             summary(cluster_lmers$pup_clust1)

emmeans::emmeans(cluster_lmers$hrdif_clust2, pairwise~y_kmeans, adjust = "bonf")
summary(cluster_lmers$hrdif_clust2)

cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 
                               (1 | ssid)+
                               (1|stimIAPS),
                             REML = FALSE,
                             data = clustering3)

                             summary(cluster_lmers$scr_clust2)

emmeans::emmeans(cluster_lmers$scr_clust2, pairwise~y_kmeans, adjust = "bonf")
summary(cluster_lmers$hrdif_clust2)
